### 2021-08-13 paper/paper.tex
Remove parens since sentence makes no sense without them
established -> mature

We are broadly interested in simulation-focused scientific computing, in particular
numerical approximations for hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD to general multi-physics coupling strategies to the development and analysis of the high-order numerical methods
our simulations are built upon. In addition, we are academics and involved in teaching
students in these areas of science. Thus, we would like to have a
code that is
\begin{enumerate}
  \item extensible for research and development,
  \item easy to apply/understand for students/collaborators,
  \item fast enough for applied 3D problems.
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia} (accessed 2021-08-11)}
and wish to include all these features within a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{\url{https://github.com/trixi-framework/Trixi.jl}}, providing adaptive
high-order numerical simulations of hyperbolic PDEs
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.

>>>>

We are broadly interested in simulation-focused scientific computing, in particular
numerical approximations for hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD to general multi-physics coupling strategies to the development and analysis of high-order numerical methods
our simulations are built upon. In addition, we are academics and involved in teaching
students in these areas of science. Thus, we would like to have a
code that is
\begin{enumerate}
  \item extensible for research and development,
  \item easy to apply/understand for students/collaborators,
  \item fast enough for applied 3D problems.
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia} (accessed 2021-08-11)}
and wish to include all these features within a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{\url{https://github.com/trixi-framework/Trixi.jl}}, providing adaptive
high-order numerical simulations of hyperbolic PDEs
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.
